Hydrodynamics of a Semipermeable Inextensible Membrane Under Flow and Confinement

### 2021-04-28 vesicle_code/docs/permeableVes/semipermeable_vesicle.tex
started reviews

Under strong confinement we show that water permeation can be amplified
on a time scale of a few seconds as a semipermeable inextensible
membrane is squeezed through a closely-fit channel and a contracting
channel. As a semipermeable inextensible membrane goes through a long
closely-fit channel, we observe lose of water at a constant rate, and
the longer the channel the more the loss of water. In the case of a
contracting channel, we find that both permeability and the pressure
gradient across the slit must be sufficiently large for a successful
passage. Throughout these simulations the membrane tension is below the
threshold for membrane poration. Thus we expect the continuum membrane
theory to well-capture the vesicle hydrodynamics, and our simulation
results shed light on the configuration and time scales needed to
observe the effects of permeability on vesicle hydrodynamics under
confinement.

>>>>

Under strong confinement we show that water permeation can be amplified
on a time scale of a few seconds as a semipermeable inextensible
membrane is squeezed through a closely-fit channel and a contracting
channel. As a semipermeable inextensible membrane goes through a long
closely-fit channel, we observe loss of water at a constant rate, and
the longer the channel the more the loss of water. In the case of a
contracting channel, we find that both permeability and the pressure
gradient across the slit must be sufficiently large for a successful
passage. Throughout these simulations the membrane tension is below the
threshold for membrane poration. Thus we expect the continuum membrane
theory to well-capture the vesicle hydrodynamics, and our simulation
results shed light on the configuration and time scales needed to
observe the effects of permeability on vesicle hydrodynamics under
confinement.
